Phylogenetics and the human microbiome.

### 2013-09-25 sbreview.tex
Start of data section.

@@

Our actions can shift the composition of our microbiome.
Changes in diet very quickly shift its composition, and there is a strong correlation between long-term diet and microbiome \citep{wu2011linking}.
Antibiotics fundamentally disturb microbial communities, resulting in an effect that lasts for years \citep{jernberg2007long,dethlefsen2008pervasive,jakobsson2010short,dethlefsen2011incomplete}.

@@

Terminology: survey versus metagenome.
Many of these methods cross over with microbial ecology in general \citep{hugenholtz2002review} (cite this?).
% I will not be talking about manipulations of these systems, such as gnotobiotic mice and human intervention.

\subsection{Microbial community estimation using marker genes}

>>>>

\hyphenation{Ge-nome Ge-nomes Me-ta-ge-nome Me-ta-ge-nomes Ma-cro-ev-o-lu-tion-ary}

@@

Our actions can shift the composition of our microbiome.
Changes in diet very quickly shift its composition, and there is a strong correlation between long-term diet and microbiome \citep{li2009human,wu2011linking}.
Antibiotics fundamentally disturb microbial communities, resulting in an effect that lasts for years \citep{jernberg2007long,dethlefsen2008pervasive,jakobsson2010short,dethlefsen2011incomplete}.

@@

% Many of these methods cross over with microbial ecology in general \citep{hugenholtz2002review} (cite this?).
% I will not be talking about manipulations of these systems, such as gnotobiotic mice and human intervention.

It is now possible to assay microbial communities in high throughput using via sequencing.
There are two ways of doing so.
The first is to amplify a specific ``marker'' gene in the genome, and perform sequencing.
The second is to randomly shear input DNA and/or RNA and then perform sequencing directly.
Although there is some vagueness in the usage of these words, we will consistently refer to the former as a \textit{survey} and the second a \textit{metagenome}.

\subsection{Microbial community estimation using marker gene surveys}
